  
---
title: 'Assignment 1'
author: Kiss Gyula
date: 2020-11-23
output:
  prettydoc::html_pretty:
    highlight: github
---

* Find a news website or any website where you can search for a keyword and the matches return in a list.
* Create a function which downloads information from a url to dataframe from the website that you found interesting.

```{r, echo=TRUE, warning=FALSE}
library(rvest)
library(data.table)
my_url <- 'https://24.hu/page/1/?s=CEU'
get_data <- function(my_url){
    print(my_url)
    t <- read_html(my_url)
    boxes <- 
      t %>% 
      html_nodes('.m-entryPost__title')  
    
    x <- boxes[[1]]
    boxes_dfs <- lapply(boxes, function(x){
       tl <- list()
       tl[['title']] <- paste0(x %>% html_nodes('.m-entryPost__link') %>% html_text(), collapse = ' ')
       tl[['link']] <-  x %>% html_nodes('.m-entryPost__link') %>% html_attr('href')
    return(tl)
})
df <- rbindlist(boxes_dfs)
return(df)
}

```

```{r, echo=TRUE, warning=FALSE}
df <- get_data(my_url)

```


* Create a function which requires two arguments. First a keyword then a number of pages to download.
* Create the links and apply your function to the links that you created and save the dataframe into csv and rds objects.
```{r, echo=TRUE, warning=FALSE}
get_pages <- function(keyword, num_of_pages) {
  links <- 
    paste0('https://24.hu/page/', 1:num_of_pages, '/?s=', keyword )
  ret_df <- rbindlist(lapply(links, get_data))
  return(ret_df)
  
}
```

```{r, echo=TRUE, warning=FALSE}
df <- get_pages('CEU', 4)
```


```{r, echo=TRUE, warning=FALSE}
write.csv(df, 'output.csv')
saveRDS(  df, 'output.rds')
knitr::kable(df)
```

